---
title: "2025-11-28_In Class Exercise"
author: "Htet Khant Linn"
date: "2025-11-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Library Installation

```{r}
library(zoo)
library(forecast)
library(ggplot2)
library(tseries)

```

```{r}
 time <- 1:200
set.seed(123)
 seasonal <- 10*sin(2*pi*time/12) + rnorm(200)
 
 ts2 = zoo(seasonal, time)
 plot(ts2)
```


#Perform ADF test

```{r}
 adf.test(ts2)
 
```
The test yields a p-value of 0.01, which supports the conclusion that the time series is stationary and suitable for modeling.


#Perform ACF test

```{r}
acf(ts2)
 
```
The plot displays a distinct wave-like pattern, serving as evidence of strong seasonality within the data.


#Perform PACF test

```{r}
pacf(ts2)
 
```
Significant spikes at the initial lags indicate that immediate past observations are strong predictors of current values.


#Fit an automated ARIMA model

```{r}
model = auto.arima(ts2,trace=TRUE, seasonal= TRUE)

```
The automated algorithm identified an ARIMA(3,0,0) model as the best fit, utilizing the last three data points for prediction.


#Model Summary

```{r}
summary(model)

```

#Forecasting for 2 years

```{r}
forecast_future= forecast(model, h=24)
plot(forecast_future, main="Forecasted model")
```

#Ljung_Box test for model validation

```{r}
Box.test(forecast_future$residuals,type="Ljung-Box")
```
The resulting p-value is extremely low, indicating that significant patterns remain in the residuals and the model fit is not yet optimal.